---
title: "Analysis of Providers Data"
author: "Rahul Kumar"
date: "August 1, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r echo=FALSE, message=FALSE,warning = FALSE }
library("dplyr")
library("lubridate")
library(readr)
#library("tidyverse")

#------------------------------------------------------------------------------------------
# Read Patient Appointment  file from Meditech DR
#------------------------------------------------------------------------------------------

appointment_data <- read_tsv("C:\\Users\\RKUMA2\\Documents\\MY_R\\Patients_Appointment_data_All_Facilities.txt", col_names = TRUE,col_types = cols(.default = "c"))

#View(appointment_data)

#------------------------------------------------------------------------------------------
# Prep data, bring to click datetime level and calculate duration. 
#------------------------------------------------------------------------------------------
DefaultDate1 = ymd_hms("2099-12-31 00:00:00")

Patient_sorted_data <- appointment_data %>% select(DateTime,PatientID) %>%
  mutate(DateTimeCt = ymd_hms(DateTime)) %>%
  select(-DateTime) %>%
  distinct() %>%
  #group_by(PatientID,DateTimeCt) %>%
  # distinct() %>%
  group_by(PatientID) %>%
  arrange(DateTimeCt) %>%
  mutate(NextDateTimeCt = if_else(is.na(lead(DateTimeCt)),DefaultDate1,lead(DateTimeCt) ),
         FirstApptForPatDateTimeCt = min(DateTimeCt)) %>%
  arrange(PatientID,DateTimeCt)
#View(Patient_sorted_data)




#------------------------------------------------------------------------------------------
# Click Data
#------------------------------------------------------------------------------------------

library("dplyr")
library("lubridate")
library("readr")
#library("tidyverse")

#------------------------------------------------------------------------------------------
# Read person clicks file from Meditech DR
#------------------------------------------------------------------------------------------

click_data <- read_tsv("C:\\Users\\RKUMA2\\Documents\\MY_R\\All_Facilities_click_data.txt", col_names = TRUE,col_types = cols(.default = "c"))

#View(click_data)


#------------------------------------------------------------------------------------------
# Prep data, bring to click datatime level and calculate duration. 
#------------------------------------------------------------------------------------------

newclick_data <- click_data %>% select(DateTime,ScreenArea,FacilityID,Person_UnvUserID,PatientID) %>%
  mutate(DateTimeCt = ymd_hms(DateTime)) %>%
  select(-DateTime) %>%
  distinct() %>%
  group_by(FacilityID,Person_UnvUserID,PatientID,DateTimeCt) %>%
  arrange(ScreenArea) %>%
  mutate(ScreenAreaList = paste0(ScreenArea, collapse = ", ")) %>%
  select(-ScreenArea) %>%
  distinct() %>%
  group_by(FacilityID,Person_UnvUserID) %>%
  arrange(DateTimeCt) %>%
  mutate(DurationMinutesRaw = as.numeric(difftime(lead(DateTimeCt),DateTimeCt,units="mins")),
         DurationMinutes = if_else(DurationMinutesRaw > 10 | is.na(DurationMinutesRaw),2,DurationMinutesRaw),
         PrevDateTimeCt = lead(DateTimeCt))  %>%
  arrange(Person_UnvUserID,DateTimeCt)
#View(newclick_data)


#------------------------------------------------------------------------------------------
# Filter out NAs and calculate working hours. 
#------------------------------------------------------------------------------------------

dfPerson_ScrArea_WorkHrs = newclick_data %>%
  filter(!is.na(DurationMinutes)) %>%
  mutate(HourOfDay = hour(DateTimeCt),
         WorkingHours = if_else(HourOfDay %in% 7:17,"NormalHrs","OffHrs")) 

#View(dfPerson_ScrArea_WorkHrs)


#-----------------------------------------------------------------------------------------
# Work Hour stats
#-----------------------------------------------------------------------------------------

dfPerson_WorkHrs_Stats = dfPerson_ScrArea_WorkHrs %>%
  group_by(Person_UnvUserID,WorkingHours) %>%
  summarise(meanDur = mean(DurationMinutes,na.rm = TRUE),
            maxDur = max(DurationMinutes,na.rm = TRUE),
            minDur = min(DurationMinutes,na.rm = TRUE),
            sumDur = sum(DurationMinutes,na.rm = TRUE))

#View(dfPerson_WorkHrs_Stats)


#------------------------------------------------------------------------------------------
# Summarize Screen Area Stats 
#------------------------------------------------------------------------------------------

dfScrArea_Stats = dfPerson_ScrArea_WorkHrs %>%
  group_by(ScreenAreaList) %>%
  summarise(meanDur = mean(DurationMinutes,na.rm = TRUE),
            maxDur = max(DurationMinutes,na.rm = TRUE),
            minDur = min(DurationMinutes,na.rm = TRUE),
            sumDur = sum(DurationMinutes,na.rm = TRUE)) %>%
  ungroup()%>%
  arrange(desc(sumDur))%>%
  top_n(10)

#View(dfScrArea_Stats)

```

 Data containing Date and Time of appointments for all Patients in 7 facilities  i.e  

1)A.AFP - Hancock Family Med-Boyd.  
2)A.FFP - Hancock Family Med-Clearview.  
3)A.HFP - Hancock Family Med-McKenzie.  
4)A.KHC - Knightstown Health Clinic.  
5)A.NGR - Hancock Internal Med-Memorial.    
6)A.NMC - Hancock Internal Med-Clearview.  
7)A.NPFM- Hancock Family Med-New Pal.    
is considered for the months of June and July i.e 2018-05-01 to 2018-07-01.

Then the audit data related to click by various providers on various screens for different patients is analysed.

Duration is calculated by looking at the time between clicks - Where click time was more than 10 mins that calculated duration is set to 2 mins.

 
7:00 am to 5:59 pm is considered as Normal Hours and other as Off hours for Providers.

By analysing timings of click we derived how much each provider is working Off Hours and Normal Hours.    
  
Initial data used for analysis:    


```{r echo=FALSE, message=FALSE,warning = FALSE}
library(knitr)
library(kableExtra)

newclick_data %>% ungroup() %>% filter(row_number() <= 2) %>% kable() %>% kable_styling()  
  
  

#------------------------------------------------------------------------------------------
# Visualizing Working Hour Stats for Providers 
#------------------------------------------------------------------------------------------ 
options(scipen = 999)
library(ggplot2)
Work_hour_stats <- ggplot(dfPerson_WorkHrs_Stats, aes(x= WorkingHours,y=sumDur, fill=WorkingHours)) + 
  geom_bar(stat = "identity",position = position_dodge(), color="black") + 
  ggtitle("Working Hour stats for different providers") + theme_bw()+
  labs(y = "Total Duration")+
  
  facet_wrap(~Person_UnvUserID ) 
plot(Work_hour_stats)
```

<br>
<br>
<br>

####Summary of Screen Area Statistics by analysing the time spent by Providers on different screens.  
  
<br>
<br>
<br>    
    

  
    
  
```{r echo=FALSE, message=FALSE,warning = FALSE}

#------------------------------------------------------------------------------------------
# Visualizing Screen Area Stats  
#------------------------------------------------------------------------------------------ 
options(scipen = 999)
library(ggplot2)
ScrArea_stats <- ggplot(dfScrArea_Stats, aes(x= reorder(ScreenAreaList,-sumDur),y = sumDur)) +
  geom_bar(stat ="identity",position = "identity",color = "red")+
  # geom_text(aes(label = sumDur),size = 3, position = position_stack(vjust = 0.5)) +
  ggtitle("Screen Area Stats For Top 10 Screens")+
  labs(x="Screen_Areas",y="Sum_of_duration in mins") + 
  theme(axis.text.x  = element_text(angle=75,hjust=0.8,vjust=0.8),axis.title.y = element_text(angle = 0))
#facet_wrap(ScreenAreaList ~ sumDur)  
plot(ScrArea_stats)



#------------------------------------------------------------------------------------------
#Joining 
#------------------------------------------------------------------------------------------ 


library(dplyr)
library(lubridate)


#---------------------------------------------------------------------------------
# Joining Data from ScreenArea stats(click_data) and Patient Appointment data
#---------------------------------------------------------------------------------
#Joined_data <- merge(x = click_data, y = Patient_sorted_data, by = "PatientID",all.x = TRUE)
#Joined_data

Joined_data <- newclick_data %>% left_join(Patient_sorted_data, by = "PatientID") %>%
  rename(ScrClickDateTimeCt = DateTimeCt.x, ApptDateTimeCt = DateTimeCt.y,
         NextApptDateTimeCt = NextDateTimeCt ) %>%
  select(-PrevDateTimeCt)


#---------------------------------------------------------------------------------
#Filtering the rows where Click Datetime is b/w Appointment Datetime window
#---------------------------------------------------------------------------------
Joined_data_filtered = Joined_data %>%
  #select(PatientID,Person_UnvUserID,DateTime,ScreenArea) %>%
  filter((ScrClickDateTimeCt >= ApptDateTimeCt & ScrClickDateTimeCt < NextApptDateTimeCt ) |
           is.na(ApptDateTimeCt) |
           ScrClickDateTimeCt < FirstApptForPatDateTimeCt ) %>%
  arrange(Person_UnvUserID,PatientID,ScrClickDateTimeCt)
#View(Joined_data_filtered)


#---------------------------------------------------------------------------------
# Calculate days diff between Clicks and Appt Date
#---------------------------------------------------------------------------------


Clicks_In_Relation_To_Appts = Joined_data_filtered %>%
  mutate(ApptDate = as.Date(ApptDateTimeCt) ,
         ScrClickDate = as.Date(ScrClickDateTimeCt), 
         ApptToClickDays = as.numeric(difftime(ScrClickDate,ApptDate,units="days")),
         ApptToClickDaysBins  = cut(ApptToClickDays, breaks = c(-1,0,1,2,3,4,5,15,25,35,45,55,65,75,85,95,999)) ,
         sameday_to_FourthDay = cut(ApptToClickDays, breaks = c(-1,0,1,2,3,4)),
         First_Five_Days = cut(ApptToClickDays, breaks = c(1,2,3,4,5)),
         Two_to_25 = cut(ApptToClickDays, breaks = c(2,3,4,5,15,25)),
         Fifth_to_55 = cut(ApptToClickDays, breaks = c(5,15,25,35,45,55))
         
  ) %>%
  mutate(Facility_ProviderID = paste(FacilityID,Person_UnvUserID, sep = ' - ') )



#---------------------------------------------------------------------------------
#Handling NA's 
#---------------------------------------------------------------------------------

Clicks_WithOut_NA =  Clicks_In_Relation_To_Appts %>%
  filter(!is.na(ApptToClickDaysBins))

#Clicks_WithOut_NA

```
<br>
<br>
<br>

####Patient Appointment Data:  

```{r echo=FALSE, message=FALSE,warning = FALSE}
Patient_sorted_data %>% ungroup() %>% filter(row_number() <= 5) %>% kable() %>% kable_styling()


```
<br>
<br>
Then the Click data of Providers is joined with this Appointment data of Patients as both had Patient ID in common.


Then the difference between the click by Provider and the Appointment days is calculated, to see gap between the appointment day and the Click by the Provider.  

So we created bins for time gaps.  

For example: (0,1] means just day 1   
(35,45] means day 36 to 45.

###Plot of Clicks vs the Days difference is :





```{r echo=FALSE, message=FALSE,warning = FALSE}

#---------------------------------------------------------------------------------
# Plotting Number Of Clicks vs ApptToClickDaysBins
#--------------------------------------------------------------------------------- 

library(ggplot2)
Clicks_stats <- ggplot(Clicks_WithOut_NA,aes(x = ApptToClickDaysBins ))  +
  geom_bar(stat ="count", color="black") +
  labs(y = "Nbr of Clicks") +
  ggtitle("Screen Area Click Stats In Relation to Appt") + theme_bw()

Clicks_stats
```
<br>
<br>
<br>





```{r echo=FALSE, message=FALSE,warning = FALSE}

#Clicks_stats1 <- Clicks_WithOut_NA %>% filter(!is.na(sameday_to_FourthDay)) %>% 
#  ggplot(aes(x = sameday_to_FourthDay ))  +
#  geom_bar(stat ="count", color="black")  +
#  labs(y = "Nbr of Clicks") +
#  ggtitle("Screen Area Click Stats In Relation to Apptday to 4th day") + theme_bw()

#Clicks_stats1

dfScrArea_Stats = Clicks_WithOut_NA %>%
  filter(!is.na(First_Five_Days)) %>%
  #filter(ApptToClickDays %in% c(3,4,5) ) %>%
  group_by(ScreenAreaList) %>%
  summarise(sumDur = sum(DurationMinutes,na.rm = TRUE)) %>%
  ungroup()%>%
  arrange(desc(sumDur))%>%
  top_n(10)

ScrArea_stats <- ggplot(dfScrArea_Stats, aes(x= reorder(ScreenAreaList,-sumDur),y = sumDur)) +
  geom_bar(stat ="identity",position = "identity",color = "red")+
  # geom_text(aes(label = sumDur),size = 3, position = position_stack(vjust = 0.5)) +
  ggtitle("Screen Area Stats For Top 10 Screens of 1st to 5th day")+
  labs(x="Screen_Areas",y="Sum_of_duration in mins") + 
  theme(axis.text.x  = element_text(angle=75,hjust=0.8,vjust=0.8),axis.title.y = element_text(angle = 0))
#facet_wrap(ScreenAreaList ~ sumDur)  
plot(ScrArea_stats)


dfScrArea_Stats = Clicks_WithOut_NA %>%
  filter(!is.na(Two_to_25 )) %>%
  group_by(ScreenAreaList) %>%
  summarise(sumDur = sum(DurationMinutes,na.rm = TRUE)) %>%
  ungroup()%>%
  arrange(desc(sumDur))%>%
  top_n(10)

ScrArea_stats <- ggplot(dfScrArea_Stats, aes(x= reorder(ScreenAreaList,-sumDur),y = sumDur)) +
  geom_bar(stat ="identity",position = "identity",color = "red")+
  ggtitle("Screen Area Stats For Top 10 Screens of 2nd to 55th day")+
  labs(x="Screen_Areas",y="Sum_of_duration in mins") + 
  theme(axis.text.x  = element_text(angle=75,hjust=0.8,vjust=0.8),axis.title.y = element_text(angle = 0))
 
plot(ScrArea_stats)


dfScrArea_Stats = Clicks_WithOut_NA %>%
  filter(!is.na(Fifth_to_55  )) %>%
  group_by(ScreenAreaList) %>%
  summarise(sumDur = sum(DurationMinutes,na.rm = TRUE)) %>%
  ungroup()%>%
  arrange(desc(sumDur))%>%
  top_n(10)

ScrArea_stats <- ggplot(dfScrArea_Stats, aes(x= reorder(ScreenAreaList,-sumDur),y = sumDur)) +
  geom_bar(stat ="identity",position = "identity",color = "red")+
  ggtitle("Screen Area Stats For Top 10 Screens of 5th to 55th day")+
  labs(x="Screen_Areas",y="Sum_of_duration in mins") + 
  theme(axis.text.x  = element_text(angle=75,hjust=0.8,vjust=0.8),axis.title.y = element_text(angle = 0))
 
plot(ScrArea_stats)


```
















```


####Plots of Clicks vs the Days difference for Individual Providers :





```{r echo=FALSE, message=FALSE,warning = FALSE}


#---------------------------------------------------------------------------------
# Plotting for each provider
#--------------------------------------------------------------------------------- 
library("ggplot2")
library("ggforce")
for(n in seq_len(17)){
print(Clicks_stats +
  facet_wrap_paginate(~Facility_ProviderID,ncol = 1,nrow = 2, scales = "fixed", shrink = TRUE,
                    labeller = "label_value", as.table = TRUE, switch = NULL, drop = TRUE, dir = "h",
                    strip.position = "top",page = n )
  )}

```

